Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2020-12-02 ms.tex
Adding in new figure and revising some wording in caption, MC results comparison

\begin{figure}
    \centering
    \includegraphics{1m_x_pdf_residualv2_log.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at an optical depth of $1 \times 10^7$. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, results in an overall smaller fractional deviation from the Monte Carlo and a much closer match to the Monte Carlo in the wing.}
    \label{fig:sol_mc_residual}
\end{figure}

@@

In Fig. \ref{fig:sol_mc_residual}, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. We find that $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ has considerably lower fractional error with the Monte Carlo in the line wing.

>>>>

\begin{figure}
    \centering
    \includegraphics{pdf_xinit0.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, results in an overall smaller fractional deviation from the Monte Carlo and a much closer match to the Monte Carlo in the wing.}
    \label{fig:sol_mc_residual}
\end{figure}

@@

In Fig. \ref{fig:sol_mc_residual}, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.
